Intermediary

### 2024-07-18 Intermediary.Rmd
Intermediary

---
title: "Making sure the variances converge"
output:
  pdf_document: default
  html_document: default
date: "2024-07-12"
---

@@

# First example: number of trees

res1_nb <- MonteCarlo(n, 10000, circle_nb)
# Just one circle to begin with

```{r}
cat("Monte Carlo variance:", res1_nb)
# Examples:
# Monte Carlo variance: 2789037
# Monte Carlo variance: 2827317
```

res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
# Just one circle to begin with

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Examples:
# Mean of the variance of bootstrap samples: 2845120
# Mean of the variance of bootstrap samples: 2851631
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Examples:
# We get a difference of: 2.01084%
# We get a difference of: 0.8599411%
```

>>>>

---
title: "Intermediary"
output:
  pdf_document: default
date: "2024-07-18"
---

@@
